\documentclass[a4paper,10pt]{article}
\usepackage[default]{lato}
\usepackage[T1]{fontenc}
\usepackage{xcolor}
\usepackage{parskip}
\usepackage{array}
\usepackage[en-US]{datetime2}
\usepackage[absolute,overlay]{textpos}
\usepackage[left=6cm,top=2cm,right=2cm,bottom=2.5cm]{geometry}
\usepackage{hyperref}

\DTMlangsetup{ord=raise}
\definecolor{lightgray}{HTML}{999999}
\definecolor{green}{HTML}{006400}
\definecolor{orange}{HTML}{C09020}
\definecolor{purple}{HTML}{B090E0}
\definecolor{red}{HTML}{F04080}
\definecolor{blue}{HTML}{40B0D0}
\definecolor{darkblue}{HTML}{00008B}

\pagestyle{empty}
\setlength{\TPHorizModule}{1cm}
\setlength{\TPVertModule}{1cm}
\newcommand{\birthdate}{\DTMdate{1990-05-10}}
\newcommand{\supersc}[1]{\textsuperscript{#1}}
\newcommand{\follownote}[1]{--- {\footnotesize\color{darkblue}#1}}
\newcommand{\tasks}{{\footnotesize\color{darkblue}Tasks}}
\newcommand{\tech}{{\footnotesize\color{darkblue}Technologies}}
\newcommand{\prog}{{\footnotesize\color{green}Programming Language:}}
\newcommand{\os}{{\footnotesize\color{green}Operating System:}}
\newcommand{\vcs}{{\footnotesize\color{green}Version Controls:}}
\newcommand{\issue}{{\footnotesize\color{green}Issue Tracking:}}
\newcommand{\acmicpcnote}[2]{--- {\footnotesize\color{darkblue}
	\href{https://icpc.baylor.edu/regionals/finder/#1/standings}
	{#2}
}}
\newcommand{\codejamnote}[2]{--- {\footnotesize\color{darkblue}
	\href{https://codingcompetitions.withgoogle.com/codejam/round/#1}
	{#2}
}}
\newcolumntype{N}{@{}m{0pt}@{}}

\begin{document}
{\Huge Ali Farzanrad}

\begin{textblock}{3.8}(1.5, 4)
	\raggedleft
	\section*{Languages}

	Native Persian \\
	Advanced in English

	\section*{Operating Systems}

	OpenBSD \\
	Linux Distros \\
	Windows

	\section*{Programming}

	System Programmer \\
	Android Developer \\
	Web Developer

\end{textblock}

\section*{\color{purple}About}

\begin{tabular}{rl}
Birth Date: & {\birthdate} \\
Phone:	& +98 911 871 3396 \\
Email:	& \href{mailto:ali_farzanrad@riseup.net}
	    {ali\_farzanrad@riseup.net} \\
Links:	& \href{https://linkedin.com/in/ali-farzanrad-0635959b}
	    {LinkedIn} \\
	& \href{https://github.com/fmwviormv}{GitHub}
\end{tabular}

\section*{{\color{red}Education}}
\begin{tabbing}
\hspace{2.5cm}\=\kill
2012--2014 \>\parbox[t]{10.5cm}{
	\textbf{M.Sc.\ in Computer Science}
	\follownote{Amirkabir University of Technology}

	Specialization in Intelligence Systems

	\begin{tabular}{p{1.5cm}p{8cm}}
	\textsc{Gpa}: & 15.07/20 \\
	\textsc{Thesis}: & ``Covering Points by Staircase Polygon'' \\
	\textsc{Advisor}: & Prof.\ Ali Mohades Khorasani
	\end{tabular}
} \\[2mm]
2008--2012 \>\parbox[t]{10.5cm}{
	\textbf{B.Sc.\ in Computer Science}
	\follownote{Amirkabir University of Technology}

	\begin{tabular}{p{1.5cm}p{8cm}}
	\textsc{Gpa}: & 15.8/20 \\
	\textsc{Thesis}: & Fast Polynomial Time Reduction
	    Between Four Different Problems in Binary Quadratic
	    Equations \\
	\textsc{Advisor}: & Prof.\ Mehdi Ghatee
	\end{tabular}
} \\[2mm]
\end{tabbing}

\section*{{\color{blue}Interests}}
\begin{itemize}
	\item Low level programming (C, socket programming, libevent)
	\item Concurrency (event-based, multi-threading, mutex/semaphore)
	\item Algorithms (graph, geometry, compiler)
\end{itemize}

\section*{{\color{orange}Awards and \emph{Honors}}}
\begin{tabbing}
\hspace{1.5cm}\=\kill
2017 \>\parbox[t]{11.5cm}{
	Ranked 474\supersc{th} among over 25\,000 contestants
	\codejamnote{0000000000201900}{Google CodeJam Round 2}
} \\[2mm]
2015 \>\parbox[t]{11.5cm}{
	Ranked 2\supersc{nd} in Ph.D. enterance exam
	\follownote{National University Entrance Exam}
} \\[2mm]
2013 \>\parbox[t]{11.5cm}{
	Ranked as 2\supersc{nd} university among all
	national universities
	\acmicpcnote{Tehran-2013}
	{ACM-ICPC Asia Tehran Regional Contest}
} \\[2mm]
2013 \>\parbox[t]{11.5cm}{
	Ranked 67\supersc{th} among over 2\,000 universities
	\follownote{The 37\supersc{th} ACM-ICPC World Finals}
} \\[2mm]
2012 \>\parbox[t]{11.5cm}{
	Ranked 1\supersc{st} among 66 teams
	\acmicpcnote{Kanpur-2012}
	{ACM-ICPC Asia Kanpur Regional Contest}
} \\[2mm]
2012 \>\parbox[t]{11.5cm}{
	Ranked 6\supersc{th} in M.Sc. enterance exam
	\follownote{National University Entrance Exam}
} \\[2mm]
2011 \>\parbox[t]{11.5cm}{
	Ranked 4\supersc{th} among 76 teams 
	\acmicpcnote{Tehran-2011}
	{ACM-ICPC Asia Tehran Regional Contest}
} \\[2mm]
2007 \>\parbox[t]{11.5cm}{
	Rewarded as Silver in National Olympiad in Informatics
} \\[2mm]
\end{tabbing}

\section*{{\color{green}Academic \emph{Experience}}}
\begin{tabbing}
\hspace{1.5cm}\=\kill
2017 \>\parbox[t]{11.5cm}{
	Problem Designer and Test Designer for Pre-Regional ACM-ICPC
	programming contest
	\follownote{Amirkabir University of Technology}
} \\[2mm]
2015 \>\parbox[t]{11.5cm}{
	Attendee in 7\supersc{th} \href{http://wscg.aut.ac.ir}
	{Winter School on Computational Geometry}
	\follownote{Amirkabir University of Technology}
} \\[2mm]
2013 \>\parbox[t]{11.5cm}{
	Teaching Assistant in Operating System
	\follownote{Amirkabir University of Technology}
} \\[2mm]
\end{tabbing}

\section*{{\color{red}Professional \emph{Experience}}}
\begin{tabbing}
\hspace{2.5cm}\=\hspace{3.5cm}\=\kill
2020--current \>Mahsan \\
\tasks \>\parbox[t]{10.5cm}{
	Developing command-line interface for company's products,
	specially for firewall management.

	Command-line is responsible for interacting with user through
	system serial console and remote ssh pty session.

	User commands varies from system configuration and diagnostic
	to network utilities with support for auto-completion and
	smart error handling (with nice user understandable messages).
} \\
\tech\>\prog\> Python 3 \\
\>\os\> Ubuntu \\
\>\vcs\> Git \\
\>\issue\> Gitlab \\[2mm]
2019--2020 \>JAM Persia \\
\tasks \>\parbox[t]{10.5cm}{
	Developing product-planning algorithm for company's ERP system.

	The algorithm is responsible for finding best selection and
	schedule of resources to produce required products in time.
} \\
\tech\>\prog\> C\# \\
\>\os\> Windows \\
\>\vcs\> SVN \\
\>\issue\> Jira \\[2mm]
2017--2018 \>Maharan International \\
\tasks \>\parbox[t]{10.5cm}{
	Developing Train Control System based on ERTMS specifications.

	We were developing core functionalities for processing and
	sending high-level signals.
} \\
\tech\>\prog\> C with Frama-C \\
\>\os\> Windows \\
\>\vcs\> TFS \\
\>\issue\> Microsoft Project \\[2mm]
2012--2016 \>Negasht Co. \\
\tasks \>\parbox[t]{10.5cm}{
	Developing web-based applications with maps and POI data.

	Developing web-services for generating map tiles.

	Developing web-services for generating static maps from vectors.

	Developing web-services for finding shortest path by giving a
	simple pair of latitude and longitudes.

	Developing an Android app with so many different survey forms.
} \\
\tech\>\prog\> C\#, JavaScript, C++, and Java \\
\>\os\> Windows \\
\>\vcs\> Microsoft Visual SourceSafe \\
\>\issue\> Company-specific issue tracker \\[2mm]
\end{tabbing}

\section*{{\color{purple}Programming \emph{Languages}}}
\begin{itemize}
	\item C (C89/90, C99, C11, libevent, pthreads, yacc, lex)
	\item Python (Python 3.x, async)
	\item C++ (C++98, C++11, C++14)
	\item Java (Java 7, Java 8)
	\item C\# (.Net Framework 4.x, ASP.NET MVC, .Net Core 2.x \& 3.x)
	\item JavaScript (ES5.x, ES6)
	\item Assembly (6502, 8086, i386, amd64, intel/at\&t syntax,
	    SIMD)
	\item UNIX Shell (sh, ksh, bash, sed, awk)
\end{itemize}

\end{document}
